Meta-analysis

### 2019-11-05 05_MetaAnalysis.Rmd
Some ME models on the clustered spray management data

```{r}

>>>>

```{r}
slim_PM_dat <- read.csv("data/slim_PM_clusterdat.csv")
slim_PM_dat$spray_management

m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

anova(m4,m5) # m5 has a much lower AIC and significantly better model

summary(m5)
